Look, we can do something

### 2024-11-08 paper.tex
Remove two words
Improve the parameter

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottlenecks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottleneck, i.e have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottleneck and points $A$ and $C$ do not form it. If you choose a
point $O$ which lies outside of the pore and travel along the pore's boundary in
one direction (either clockwise or counter-clockwise), when you arrive at $A$
you will see the point $O$ to your left and when you are in $B$ you will see $O$
to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
the same side from you. Instead of doing this check for ``bottleneckness'', we
add a penalty coefficient to the distance between points, namely for a pair of
points $(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$ using \ref{eq:intro}:
\begin{equation}
  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
  \label{eq:pre-awesomeness}
\end{equation}
Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottleneck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}

@@

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``\highlight{awesomeness}'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2\}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ and $B$ are the elongation the boundary of the pore,
$\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
the length of a path (the shortest one) between $A$ and $B$ along the boundary.

@@

Flaws of this parameter include:
\begin{itemize}
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
  are otherwise clusterized correctly.
\item Small changes to an image of a pore, when cleverly done, can make drastic
  changes in \highlight{awesomeness}.
\end{itemize}

@@

The second flaw means that a pore with a very small attachment (compared to the
pore's total surface) connected with a thin throat to the pore's main body has
low \highlight{awesomeness}, like the third pore on \cref{fig:small-blob}, a row
on the top. Normally, small attachments like this do not contribute to any
physical process in any way, so they can simply be ignored and, therefore, their
impact on \highlight{awesomeness} may be not justified.

>>>>

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottlenecks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottleneck, i.e have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottleneck and points $A$ and $C$ do not. If you choose a point $O$
which lies outside of the pore and travel along the pore's boundary in one
direction (either clockwise or counter-clockwise), when you arrive at $A$ you
will see the point $O$ to your left and when you are in $B$ you will see $O$ to
your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to the
same side from you. Instead of doing this check for ``bottleneckness'', we add a
penalty coefficient to the distance between points, namely for a pair of points
$(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$ using \ref{eq:intro}:
\begin{equation}
  p = \inf \{ p_{AB} \ \forall (A, B) \in B^2 : 2 L_{AB} \ge cP \}
  \label{eq:pre-awesomeness}
\end{equation}
The condition on a pair of points $(A, B)$ is that the ``boundary distance''
between them must be no less than $\frac{cP}{2}$ where $P$ is a perimeter of a
pore and $c \in [0,1]$ is some parameter. This parameter is introduced to
prevent small features of the boundary from affecting $p$. In this paper we will
use $c = 0.1$. A value $c = 0$ means there are no restrictions on $(A, B)$.

Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottleneck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}

@@

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``\highlight{awesomeness}'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2 : 2
    L_{AB} \ge cP \}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ and $B$ are the elongation and the boundary of the pore,
$\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
the length of a path (the shortest one) between $A$ and $B$ along the boundary.

@@

Flaws of this parameter include:
\begin{itemize}
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
  are otherwise clusterized correctly.
\end{itemize}

@@
